Postural developments mediate children's visual access to social information

### 2018-01-29 writeup-cogsci/cogsci2018_faceOnly_alessandro.Rmd
wrist detection corrections

### Detector evaluation
To evaluate face detector performance, we needed to construct an unbiased "gold set" of labeled frames that made sure to account for the relatively rare appearance of faces in the dataset. We thus hand-labeled two samples: a sample containing a high density of faces (half reported by MTCNN, half by OpenPose) and a random sample from the remaining frames. Each sample was comprised of an equal number of frames taken from each participant (i.e., video). Faces were classifed as present in a frame if at least half of the face was showing. Precision (hits / hits + false alarms), recall (hits / hits + misses), and F-score (harmonic mean of precision and recall) were calculated for all detectors and are reported in Table 2. For wrist detections, the "gold set" was constructed in the same manner, with the exception that frames with a high density of wrists were taken by wrist detections made by OpenPose.

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}
### READ IN DETECTIONS
getwd()
d <- read_feather("../data/consolidated_data_4detectors.feather") %>%
  mutate(posture = factor(posture), orientation = factor(orientation))

@@

\begin{table}[ht]
\centering
\begin{tabular}{rllrrr}
  \hline
   Algorithm & Sample\ Type & P & R & F \\ 
  \hline
  MTCNN-Faces & High density & 0.89 & 0.92 & \textbf{0.90} \\ 
  MTCNN-Faces & Random & 0.94 & 0.62 & 0.75 \\ 
  OpenPose-Faces & High density & 0.78 & 0.93 & 0.84 \\ 
  OpenPose-Faces & Random & 0.72 & 0.80 & \textbf{0.76} \\ 
  ViolaJones-Faces & High density & 0.96 & 0.44 & 0.60 \\ 
  ViolaJones-Faces & Random & 0.44 & 0.38 & 0.41 \\ 
  OpenPose-Wrists & High density & 0.64 & 1.00 & 0.78 \\ 
  OpenPose-Wrists & Random & 0.76 & 0.26 & 0.39 \\ 
   \hline
\end{tabular}
\caption{Detector performance on both high density samples (where proportion of faces detected was high) and random samples (where frames were randomly selected). P, R, and F denote precision, recall, and F-score, respectively. Scores in bold are the highest F-scores for each sample type.} 
\end{table}

>>>>

### Detector evaluation
To evaluate face detector performance, we needed to construct an unbiased "gold set" of labeled frames that made sure to account for the relatively rare appearance of faces in the dataset. We thus hand-labeled two samples: a sample containing a high density of faces (half reported by MTCNN, half by OpenPose) and a random sample from the remaining frames. Each sample was comprised of an equal number of frames taken from each participant (i.e., video). Faces were classifed as present in a frame if at least half of the face was showing. Precision (hits / hits + false alarms), recall (hits / hits + misses), and F-score (harmonic mean of precision and recall) were calculated for all detectors and are reported in Table 2. For wrist detections, the "gold set" was constructed in the same manner, with the exception that frames with a high density of wrists were taken by pose detections made by OpenPose.

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}
### READ IN DETECTIONS
d <- read_feather("../data/consolidated_data_4detectors.feather") %>%
  mutate(posture = factor(posture), orientation = factor(orientation))

@@

\begin{table}[ht]
\centering
\begin{tabular}{rllrrr}
  \hline
   Algorithm & Sample\ Type & P & R & F \\ 
  \hline
  MTCNN-Faces & High density & 0.89 & 0.92 & \textbf{0.90} \\ 
  MTCNN-Faces & Random & 0.94 & 0.62 & 0.75 \\ 
  OpenPose-Faces & High density & 0.78 & 0.93 & 0.84 \\ 
  OpenPose-Faces & Random & 0.72 & 0.80 & \textbf{0.76} \\ 
  ViolaJones-Faces & High density & 0.96 & 0.44 & 0.60 \\ 
  ViolaJones-Faces & Random & 0.44 & 0.38 & 0.41 \\ 
  OpenPose-Wrists & High density & 0.66 & 1.00 & 0.79 \\ 
  OpenPose-Wrists & Random & 0.88 & 0.29 & 0.43 \\ 
   \hline
\end{tabular}
\caption{Detector performance on both high density samples (where proportion of faces detected was high) and random samples (where frames were randomly selected). P, R, and F denote precision, recall, and F-score, respectively. Scores in bold are the highest F-scores for each sample type.} 
\end{table}

### 2018-01-29 writeup-cogsci/cogsci2018_faceOnly_alessandro.tex
wrist detection corrections

For wrist detection, OpenPose performed moderately well (F = 0.72) with
relatively high precision, but low recall on the randomly sampled set of
frames (see Table 2). We thus analyze wrist detections, with the caveat
that we are likely underestimating the proportion of wrists overall in
the datatset.

@@

To formalize these observations, we fit a generalized linear model to
the proportion of faces infants saw in each posture and orientation (as
detected by MTCNN), with participant's age, orientation, and posture as
independent variables. A summary of the coefficients of a model with
only main effects (and no interactions) model can be found in Table 3.
When we did include interaction terms between age, posture, and
orientation, age no longer remained a significant predictor (b = -15.84,
SE = 113.98, z = -0.14 , p =0.89). We found the same pattern of results
for the OpenPose face detections, omitted here for brevity. We also
found the same pattern with respect to infant's visual access to hands
(see Table 4); including interaction terms also reduced any main effect
of age on the proportion of hands detected (b = -15.7, SE = 113.98, z =
-0.14 , p =0.89). Thus, these results suggest that infants' access to
social information is heavily influenced by their postural and
locomotive development.

@@

Finally, we analyzed how face and wrists detections changed during
object labeling events as a function of infant's posture and
orientation. Specfically, we analyzed a four-second window around each
labeling event (e.g., ``Look at the {[}zem{]}!''); these labeling events
were hand-annotated and automatically synchronized with the
frame-by-frame face detections. We again found that infants' posture and
orientations impacted the degree to which they saw their caregiver's
face and wrist during a labeling event; infants who were sitting or
standing were more likely to have access to this social information.

>>>>

For wrist detection, OpenPose performed moderately well (F = 0.74) with
relatively high precision, but low recall on the randomly sampled set of
frames (see Table 2). We thus analyze wrist detections, with the caveat
that we are likely underestimating the proportion of wrists overall in
the datatset.

@@

To formalize these observations, we fit a generalized linear model to
the proportion of faces infants saw in each posture and orientation (as
detected by MTCNN), with participant's age, orientation, and posture as
independent variables. A summary of the coefficients of a model with
only main effects (and no interactions) model can be found in Table 3.
When we did include interaction terms between age, posture, and
orientation, age no longer remained a significant predictor (b = -15.84,
SE = 113.98, z = -0.14 , p = 0.89). We found the same pattern of results
for the OpenPose face detections, omitted here for brevity. We also
found the same pattern with respect to infant's visual access to hands
(see Table 4); including interaction terms also eliminated any main
effect of age on the proportion of hands detected (b = -15.7, SE =
113.98, z = -0.14, p = 0.89). Thus, these results suggest that infants'
access to social information is heavily influenced by their postural and
locomotive development.

@@

Finally, we analyzed how face and wrist detections changed during object
labeling events as a function of infant's posture and orientation.
Specfically, we analyzed a four-second window around each labeling event
(e.g., ``Look at the {[}zem{]}!''); these labeling events were
hand-annotated and automatically synchronized with the frame-by-frame
face detections. We found that infants' posture and orientations
impacted the degree to which they saw their caregiver's face and wrist
during a labeling event; infants who were sitting or standing were more
likely to have access to this social information. However, this did not
manifest in a direct change the presence of wrists/hands before
vs.~after naming events (average difference in proportion of wrists
detected, 8 m.o. = -0.006, 12 m.o. = -0.013, 16 m.o. = -0.007) or in
proportion of faces detected (average difference in proportion of faces
detected, 8 m.o. = -0.002, 12 m.o. = 0, 16 m.o. = -0.004).
